Dominance Regions for Rank Two Cluster Algebras

### 2022-05-19 dominance_regions.tex
Obsessing about the figures
Obsessing even more

\begin{figure}[h!]
  \centering
    \newcommand{\setconstants}{
      \tikzmath{\b = 3; \c = 6 / \b; \s = sqrt(\b * \c * (\b * \c -4)); \bcmo = \b * \c - 1; \bcms = \b * \c - \s; \bcps = \b * \c + \s;}
      \tikzmath{ \xmin = -6; \xmax = 5; \ymin = -4; \ymax = 8;}
      \clip ({\xmin-0.2},{\ymin-0.2}) rectangle ({\xmax+0.2},{\ymax+0.2});
    }
    \newcommand{\boundingrays}{
      \draw [color=lightgray, thick] (2*\xmin,0) -- (2*\xmax,0);
      \draw [color=lightgray, thick] (0,2*\ymin) -- (0, 2*\ymax);
      \draw [color=lightgray, thick, dashed] (0,0) -- (2*\xmax, -\xmax * \bcms / \b); 
      \draw [color=lightgray, thick, dashed] (0,0) -- ( - 4 * \b * \ymin / \bcps, 2*\ymin); 
    }
  \begin{tikzpicture}[scale=.5]
      \setconstants;
      \foreach \x in {\xmin,...,\xmax} {
        \foreach \y in {\ymin,...,\ymax} {
          \fill[color=gray] (\x,\y) circle (0.05);
        }
      };
      \tikzmath{ \x=4; \y=-3;};
      \boundingrays;
      \fill [fill=gray!30, fill opacity=0.4] (\x,\y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- cycle;
      \fill [fill=red!30, fill opacity=0.5]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y)  -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- ({\bcms/(2*\c)*\y+\x},0) --  (0,{\bcps/(2*\b)*(\x+\b*\y)+(-\c*\x - \b*\c*\y + \y)}) -- cycle;
      \fill [fill=darkgreen!30, fill opacity=0.5] (\x,\y) -- ({\x+\bcps/(2*\c)*\y},0) -- ({\bcps/(2*\s)*(2*\x+\b*\y)},{\bcps/(2*\s)*(\c*\x+2*\y)}) -- (0,{\bcps/(2*\b)*\x+\y}) -- cycle;
      \draw [red, thick, join=round]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y)  -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- ({\bcms/(2*\c)*\y+\x},0) -- (0,{\bcps/(2*\b)*(\x+\b*\y)+(-\c*\x - \b*\c*\y + \y)}) -- cycle;
      \draw [darkgreen, thick, join=round] (\x,\y) -- ({\x+\bcps/(2*\c)*\y},0) -- ({\bcps/(2*\s)*(2*\x+\b*\y)},{\bcps/(2*\s)*(\c*\x+2*\y)}) -- (0,{\bcps/(2*\b)*\x+\y}) -- cycle;
      \draw [thick, join=round] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y);;
      \draw [thick, dotted, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) --  (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
      \draw [thick, dashed, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
      \draw [thick, fill=white]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt) node[above left]{$\lambda'$};
      \fill (\x , \y)  circle (5pt) node[below right]{$\lambda$};
      \foreach \x/\y in { 1/-3, -2/-3, -5/-3, -2/-1, -5/-1, -5/1, -2/3, -5/3, -2/5, -5/5 } {
        \draw[color=blue, fill=white] (\x,\y) circle (4pt);
      };
      \foreach \x/\y in { 1/-1, 1/1, -2/1 } {
        \fill[color=blue] (\x,\y) circle (4pt);
      };
      \draw (-3.5,-3.5) node{$\cS_\lambda$};
      \draw [darkgreen](2.5,1) node{$\cP_\lambda$};
      \draw [red](-2,6.5) node{$\cP'_\lambda$};
  \end{tikzpicture}
\end{figure}
  \section{Introduction}
  Cluster algebras were introduced by Fomin and Zelevinsky as a tool in the study of Lusztig's dual canonical bases.
  Since their inception they have found application in a variety of different areas in mathematics, nevertheless a fundamental problem in the theory remains constructing bases with ``good'' properties.

@@

      \draw [color=lightgray, thick] (2*\xmin,0) -- (2*\xmax,0);
      \draw [color=lightgray, thick] (0,2*\ymin) -- (0, 2*\ymax);
      \draw [color=lightgray, thick] (0,0) -- (2*\xmax, -2*\xmax / \b);
      \draw [color=lightgray, thick] (0,0) -- (2*\xmax, -2*\xmax * \c / \bcmo );
      \draw [color=lightgray, thick, dashed] (0,0) -- (2*\xmax, -\xmax * \bcms / \b); 
      \draw [color=lightgray, thick, dashed] (0,0) -- ( - 4 * \b * \ymin / \bcps, 2*\ymin); 

@@

      \tikzmath{ \t=5; \r=1; \q=2; \xx={\r*\b+\q*(\b*\c-1) }; \yy = {-\r -\c*\q};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }

@@

      \draw [thick, dash dot, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);

@@

      \draw [thick, dotted, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) --  (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
      \draw [thick, dashed, join=round] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);

@@

      \draw [color=lightgray, thick] (2*\xmin,0) -- (2*\xmax,0);
      \draw [color=lightgray, thick] (0,2*\ymin) -- (0, 2*\ymax);

@@

      \draw [color=lightgray, thick, dashed] (0,0) -- (2*\xmax, -\xmax * \bcms / \b); 
      \draw [color=lightgray, thick, dashed] (0,0) -- ( - 4 * \b * \ymin / \bcps, 2*\ymin); 

@@

  The support $\cG_\lambda$ of the greedy basis element of $\cA(b,c)$ with $\bfg$-vector $\lambda$ is well-known \cite{LLZ,cgmmrsw}.
  This is indicated by the solid and dashed lines in Theorem~\ref{th:maximum support} where dashed lines indicate points that are excluded from the support (note that the white dot does not indicate that this point is excluded).
  For our purposes, it is enough to observe the following closure property for the greedy support.
  \begin{definition}
    A subset $\cS\subset\RR^2$ is called \emph{min-convex} if $\lambda,\mu\in\cS$ implies the segments joining $\lambda$ and $\mu$ to $\big(\min(\lambda_0,\mu_0),\min(\lambda_1,\mu_1)\big)$ are contained in $\cS$.
  \end{definition}
  In particular, (an upper bound for) the greedy support can be found using the $\bfg$-vector $\lambda$ indicated by a black dot and the opposite $\bfg$-vector $\lambda'$ indicated by a white dot in Theorem~\ref{th:maximum support}.
  Write $\overline{\cG}_\lambda$ for the downward scaling of the min-convex closure of $\{\lambda,\lambda'\}$, that is $\overline{\cG}_\lambda$ contains the segments joining $\lambda$ and $\lambda'$ with $\big(\min(\lambda_0,\lambda'_0),\min(\lambda_1,\lambda'_1)\big)$ and for any $\mu\in\overline{\cG}_\lambda$ we have $t\mu\in\overline{\cG}_\lambda$ for $0\le t\le 1$.
  Clearly, $\cG_\lambda\subset\overline{\cG}_\lambda$.

>>>>

\begin{figure}[h!]
  \centering
    \newcommand{\setconstants}{
      \tikzmath{\b = 3; \c = 6 / \b; \s = sqrt(\b * \c * (\b * \c -4)); \bcmo = \b * \c - 1; \bcms = \b * \c - \s; \bcps = \b * \c + \s;}
      \tikzmath{ \xmin = -6; \xmax = 5; \ymin = -4; \ymax = 8;}
      \clip ({\xmin-0.2},{\ymin-0.2}) rectangle ({\xmax+0.2},{\ymax+0.2});
    }
    \newcommand{\boundingrays}{
      \draw [color=gray, thick] (2*\xmin,0) -- (2*\xmax,0);
      \draw [color=gray, thick] (0,2*\ymin) -- (0, 2*\ymax);
      \draw [color=gray, thick, dashed] (0,0) -- (2*\xmax, -\xmax * \bcms / \b); 
      \draw [color=gray, thick, dashed] (0,0) -- ( - 4 * \b * \ymin / \bcps, 2*\ymin); 
    }
  \begin{tikzpicture}[scale=.5]
      \setconstants;
      \tikzmath{ \x=4; \y=-3;};
      \fill [fill=black!30, fill opacity=0.4] (\x,\y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- cycle;
      \fill [fill=red!30, fill opacity=0.5]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y)  -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- ({\bcms/(2*\c)*\y+\x},0) --  (0,{\bcps/(2*\b)*(\x+\b*\y)+(-\c*\x - \b*\c*\y + \y)}) -- cycle;
      \fill [fill=darkgreen!30, fill opacity=0.5] (\x,\y) -- ({\x+\bcps/(2*\c)*\y},0) -- ({\bcps/(2*\s)*(2*\x+\b*\y)},{\bcps/(2*\s)*(\c*\x+2*\y)}) -- (0,{\bcps/(2*\b)*\x+\y}) -- cycle;
      \foreach \x in {\xmin,...,\xmax} {
        \foreach \y in {\ymin,...,\ymax} {
          \fill[color=gray] (\x,\y) circle (0.05);
        }
      };
      \boundingrays;
      \draw [red, thick, join=round]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y)  -- (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) -- ({\bcms/(2*\c)*\y+\x},0) -- (0,{\bcps/(2*\b)*(\x+\b*\y)+(-\c*\x - \b*\c*\y + \y)}) -- cycle;
      \draw [darkgreen, thick, join=round] (\x,\y) -- ({\x+\bcps/(2*\c)*\y},0) -- ({\bcps/(2*\s)*(2*\x+\b*\y)},{\bcps/(2*\s)*(\c*\x+2*\y)}) -- (0,{\bcps/(2*\b)*\x+\y}) -- cycle;
      \draw [thick, join=round] (\x , \y) -- ( \x+\b*\y, \y) -- ( \x+\b*\y , -\c*\x - \b*\c*\y + \y);;
      %\draw [thick, join=round, line cap=round, dash pattern=on 0pt off 4\pgflinewidth] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) --  (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
      %\draw [thick, join=round, line cap=round, dash pattern=on 4\pgflinewidth off 8\pgflinewidth ] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
      \draw [thick, join=round, line cap=round, dash pattern=on 0pt off 4\pgflinewidth] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
      \draw [thick, join=round, line cap=round, dash pattern=on 4\pgflinewidth off 8\pgflinewidth ] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) --  (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);
      \draw [thick, fill=white]  ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) circle (5pt) node[above left]{$\lambda'$};
      \fill (\x , \y)  circle (5pt) node[below right]{$\lambda$};
      \foreach \x/\y in { 1/-3, -2/-3, -5/-3, -2/-1, -5/-1, -5/1, -2/3, -5/3, -2/5, -5/5 } {
        \draw[color=blue, fill=white] (\x,\y) circle (4pt);
      };
      \foreach \x/\y in { 1/-1, 1/1, -2/1 } {
        \fill[color=blue] (\x,\y) circle (4pt);
      };
      \draw (-3.5,-3.5) node{$\cS_\lambda$};
      \draw [darkgreen](2.5,1) node{$\cP_\lambda$};
      \draw [red](-2,6.5) node{$\cP'_\lambda$};
  \end{tikzpicture}
\end{figure}
  \section{Introduction}
  Cluster algebras were introduced by Fomin and Zelevinsky as a tool in the study of Lusztig's dual canonical bases.
  Since their inception they have found application in a variety of different areas in mathematics, nevertheless a fundamental problem in the theory remains constructing bases with ``good'' properties.

@@

      \draw [color=gray, thick] (2*\xmin,0) -- (2*\xmax,0);
      \draw [color=gray, thick] (0,2*\ymin) -- (0, 2*\ymax);
      \draw [color=gray, thick] (0,0) -- (2*\xmax, -2*\xmax / \b);
      \draw [color=gray, thick] (0,0) -- (2*\xmax, -2*\xmax * \c / \bcmo );
      \draw [color=gray, thick, dashed] (0,0) -- (2*\xmax, -\xmax * \bcms / \b); 
      \draw [color=gray, thick, dashed] (0,0) -- ( - 4 * \b * \ymin / \bcps, 2*\ymin); 

@@

      \tikzmath{ \t=5; \r=1; \q=1; \xx={\r*\b+\q*(\b*\c-1) }; \yy = {-\r -\c*\q};  \x={\t*\xx/sqrt((\xx)^2+(\yy)^2)}; \y={\t*\yy/sqrt((\xx)^2+(\yy)^2)}; }

@@

      \draw [thick, join=round, line cap=round, dash pattern=on 0pt off 4\pgflinewidth on 4\pgflinewidth off 4\pgflinewidth] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);

@@

      \draw [thick, join=round, line cap=round, dash pattern=on 0pt off 4\pgflinewidth] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) -- (0,0) --  (\x , \y);
      \draw [thick, join=round, line cap=round, dash pattern=on 4\pgflinewidth off 8\pgflinewidth ] ( \x+\b*\y , -\c*\x - \b*\c*\y + \y) --  (\bcps*\x/\s + \bcps*\b*\y/2/\s, -\bcps*\c*\x/2/\s - \bcps*\b*\c*\y/2/\s + \bcps*\y/\s) --  (\x , \y);

@@

      \draw [color=gray, thick] (2*\xmin,0) -- (2*\xmax,0);
      \draw [color=gray, thick] (0,2*\ymin) -- (0, 2*\ymax);
      \draw [color=gray, thick, dashed] (0,0) -- (2*\xmax, -\xmax * \bcms / \b); 
      \draw [color=gray, thick, dashed] (0,0) -- ( - 4 * \b * \ymin / \bcps, 2*\ymin); 

@@

@@

  The support $\cG_\lambda$ of the greedy basis element of $\cA(b,c)$ with $\bfg$-vector $\lambda$ is well-known \cite{LLZ,cgmmrsw}.
  This is indicated by the solid and dotted lines in Theorem~\ref{th:maximum support} where dotted lines indicate points that are excluded from the support (note that the white dot does not indicate that this point is excluded).
  For our purposes, it is enough to observe the following closure property for the greedy support.
  \begin{definition}
    A subset $\cS\subset\RR^2$ is called \emph{min-convex} if $\lambda,\mu\in\cS$ implies the segments joining $\lambda$ and $\mu$ to $\big(\min(\lambda_0,\mu_0),\min(\lambda_1,\mu_1)\big)$ are contained in $\cS$.
  \end{definition}
  In particular, (an upper bound for) the greedy support can be found using the $\bfg$-vector $\lambda$ indicated by a black dot and the opposite $\bfg$-vector $\lambda'$ indicated by a white dot in Theorem~\ref{th:maximum support}.
  Write $\overline{\cG}_\lambda$ for the downward scaling of the min-convex closure of $\{\lambda,\lambda'\}$, that is $\overline{\cG}_\lambda$ contains the segments joining $\lambda$ and $\lambda'$ with $\big(\min(\lambda_0,\lambda'_0),\min(\lambda_1,\lambda'_1)\big)$ and for any $\mu\in\overline{\cG}_\lambda$ we have $t\mu\in\overline{\cG}_\lambda$ for $0\le t\le 1$.
  Clearly, $\cG_\lambda\subset\overline{\cG}_\lambda$.
